Supplemental Materials

### 2021-07-20 supplement/supplement-main.Rmd
figure aspect ratios, observed alphas

```{r s3_plot_bystudy, echo=F, message=F, warning=F, fig.width=8, fig.height=4, fig.cap="Belief changes following the intervention in Experiments 3a and 3b. Left, mean difference scores from pretest to posttest for the 14 belief scales across experimental conditions; our primary outcome of interest, vaccination intentions, is highlighted in yellow. Right, mean observed and model predicted change scores for the Vaccine Ingredients intervention condition. In both plots, error bars represent 95\\% confidence intervals."}

@@

s3_diff_plot_bystudy <- s3_scored %>% 
  # spread(phase, mean) %>% 
  drop_na(scale) %>% 
  mutate(post = rescale_beta(post, -3, 3), pre = rescale_beta(pre, -3, 3)) %>% 
  mutate(diff = post-pre) %>% 
  mutate(
    scale = recode_nodes2(scale),
    condition = recode_factor(condition, 
                              "noInterv" = "Control",
                              .default = "Vaccine Ingredients")) %>% 
  left_join(s3_demo %>% distinct(workerId, study)) %>%
  mutate(study = recode_factor(study, "A" = "Expt. 3A", "B" = "Expt. 3B")) %>%
  group_by(study, condition, scale) %>%
  summarize(M = mean(diff, na.rm=TRUE), se = sd(diff)/sqrt(n())) %>% 
  ungroup() %>%
  left_join(s3_scale_order) %>%
  ggplot(aes(x = reorder(scale,order), y = M, ymin = M-se*2, ymax=M+se*2, 
             color = interaction(condition, study, sep = ": "), 
             shape = interaction(condition, study, sep = ": "))) +
  scale_x_discrete() +
  annotate("rect", 
           xmin = s3_scale_order %>%
             filter(grepl("intent", tolower(scale))) %>% pull(order) - 0.35,
           xmax = s3_scale_order %>%
             filter(grepl("intent", tolower(scale))) %>% pull(order) + 0.35,
           ymin = -Inf,
           ymax = Inf,
           fill = "#fffaba") +
  geom_pointrange(aes(group = interaction(condition, study)),
                  position=position_dodge(width=.4), fill = "white") +
  geom_hline(yintercept=0, linetype="dashed", color="grey") +
  scale_color_manual(values=rep(c("#0067b1","#c50024"), 2)) +
  scale_shape_manual(values=c(16, 17, 21, 24)) +
  theme_bw(base_size=11) +
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    panel.grid = element_blank(),
    legend.position = c(.5,.1),
    legend.direction = "horizontal",
    legend.background = element_rect(fill = NA),
    aspect.ratio=.5
    ) +
  labs(title="A", y = "Mean difference", x = "Belief scale", 
       color="Intervention", shape="Intervention") +
  guides(shape = guide_legend(nrow = 2, byrow = T),
         color = guide_legend(nrow = 2, byrow = T))

@@

s3_obs_pred_plot_bystudy <- bind_rows(obs_pred_A %>% mutate(study = "A"),
                                      obs_pred_B %>% mutate(study = "B")) %>%
  mutate(study = recode_factor(study, "A" = "Expt. 3A", "B" = "Expt. 3B")) %>%
  ggplot(aes(x=predicted, y = observed, ymin = ll, ymax=ul,
             shape = study)) +
  geom_abline(slope=1, intercept=0, linetype="dashed", alpha =.5) +
  geom_errorbar(alpha=.5, width=0) +
  geom_point(size=2.5, fill = "white") +
  scale_shape_manual(values=c(16, 21)) +
  # coord_fixed(ratio=1) +
  coord_cartesian(xlim=c(-.12,.08), ylim=c(-.12,.08)) +
  annotate(geom = "text", x = .05, y = -.08, 
           label = bquote(paste("r"["A"]*" = ", .(cor_val_A)))) +
  annotate(geom = "text", x = .05, y = -.105, 
           label = bquote(paste("r"["B"]*" = ", .(cor_val_B)))) +
  theme_bw(base_size=11) +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        legend.position = c(.15,.85),
        legend.background = element_rect(fill = NA)) +
  theme(aspect.ratio = 1) +
  labs(title = "B", y = "Observed change", x="Predicted change", 
       shape = "Experiment")

@@

_Holistic balance_, from McFadden et al.’s (2010) Complementary, Alternative, and Conventional Medicine Attitudes Scale (CACMAS) (Study 1 observed $\alpha$ = `r format(round(alpha_values$hb, 2), nsmall = 2)`)

@@

_Naturalism_ (Study 1 observed $\alpha$ = `r format(round(alpha_values$nat, 2), nsmall = 2)`)

@@

_Medical skepticism_ (Study 1 observed $\alpha$ = `r format(round(alpha_values$medSkept, 2), nsmall = 2)`)

@@

_Disease rarity_ (Study 1 observed $\alpha$ = `r format(round(alpha_values$diseaseRare, 2), nsmall = 2)`)

@@

_Disease severity_ (Study 1 observed $\alpha$ = `r format(round(alpha_values$diseaseSevere, 2), nsmall = 2)`)

@@

_Vaccine effectiveness_ (Study 1 observed $\alpha$ = `r format(round(alpha_values$vaccEff, 2), nsmall = 2)`)

@@

_Vaccine danger_ (Study 1 observed $\alpha$ = `r format(round(alpha_values$vaccDanger, 2), nsmall = 2)`)

@@

_Toxic additives in vaccines_ (Study 1 observed $\alpha$ = `r format(round(alpha_values$vaccTox, 2), nsmall = 2)`)

@@

_Infant immune system: Vaccines strain_ (Study 1 observed $\alpha$ = `r format(round(alpha_values$vaccStrain, 2), nsmall = 2)`)

@@

_Vaccination intentions_ (Study 1 observed $\alpha$ = `r format(round(alpha_values$vaccIntent, 2), nsmall = 2)`)

@@

_Parental expertise_ (Study 1 observed $\alpha$ = `r format(round(alpha_values$parentExpert, 2), nsmall = 2)`)

@@

_Infant immune system: Limited capacity_ (Study 1 observed $\alpha$ = `r format(round(alpha_values$infantImmLimCap, 2), nsmall = 2)`)

@@

_Infant immune system: Weakness_ (Study 1 observed $\alpha$ = `r format(round(alpha_values$infantImmWeak, 2), nsmall = 2)`)

@@

_Parental protectiveness_ (Study 1 observed $\alpha$ = `r format(round(alpha_values$overpar, 2), nsmall = 2)`)

>>>>

```{r s3_plot_bystudy, echo=F, message=F, warning=F, fig.width=10, fig.height=5, fig.cap="Belief changes following the intervention in Experiments 3a and 3b, broken out by experiment. Left, mean difference scores from pretest to posttest for the 14 belief scales across experimental conditions; our primary outcome of interest, vaccination intentions, is highlighted in yellow. Right, mean observed and model predicted change scores for the Vaccine Ingredients intervention condition. In both plots, error bars represent 95\\% confidence intervals."}

@@

s3_diff_plot_bystudy <- s3_scored %>% 
  # spread(phase, mean) %>% 
  drop_na(scale) %>% 
  mutate(post = rescale_beta(post, -3, 3), pre = rescale_beta(pre, -3, 3)) %>% 
  mutate(diff = post-pre) %>% 
  mutate(
    scale = recode_nodes2(scale),
    condition = recode_factor(condition, 
                              "noInterv" = "Control",
                              .default = "Vaccine Ingredients")) %>% 
  left_join(s3_demo %>% distinct(workerId, study)) %>%
  mutate(study = recode_factor(study, "A" = "Expt. 3A", "B" = "Expt. 3B")) %>%
  group_by(study, condition, scale) %>%
  summarize(M = mean(diff, na.rm=TRUE), se = sd(diff)/sqrt(n())) %>% 
  ungroup() %>%
  left_join(s3_scale_order) %>%
  ggplot(aes(x = reorder(scale,order), y = M, ymin = M-se*2, ymax=M+se*2, 
             color = interaction(condition, study, sep = ": "), 
             shape = interaction(condition, study, sep = ": "))) +
  scale_x_discrete() +
  annotate("rect", 
           xmin = s3_scale_order %>%
             filter(grepl("intent", tolower(scale))) %>% pull(order) - 0.35,
           xmax = s3_scale_order %>%
             filter(grepl("intent", tolower(scale))) %>% pull(order) + 0.35,
           ymin = -Inf,
           ymax = Inf,
           fill = "#fffaba") +
  geom_pointrange(aes(group = interaction(condition, study)),
                  position=position_dodge(width=.4), fill = "white") +
  geom_hline(yintercept=0, linetype="dashed", color="grey") +
  scale_color_manual(values=rep(c("#0067b1","#c50024"), 2)) +
  scale_shape_manual(values=c(16, 17, 21, 24)) +
  theme_bw(base_size=11) +
  theme(
    axis.text.x = element_text(angle=45, hjust=1),
    panel.grid = element_blank(),
    legend.position = c(.5,.15),
    legend.direction = "horizontal",
    legend.background = element_rect(fill = NA),
    aspect.ratio=.5
    ) +
  labs(title="A", y = "Mean difference", x = "Belief scale", 
       color="Intervention", shape="Intervention") +
  guides(shape = guide_legend(nrow = 2, byrow = T),
         color = guide_legend(nrow = 2, byrow = T))

@@

s3_obs_pred_plot_bystudy <- bind_rows(obs_pred_A %>% mutate(study = "A"),
                                      obs_pred_B %>% mutate(study = "B")) %>%
  mutate(study = recode_factor(study, "A" = "Expt. 3A", "B" = "Expt. 3B")) %>%
  ggplot(aes(x=predicted, y = observed, ymin = ll, ymax=ul,
             shape = study)) +
  geom_abline(slope=1, intercept=0, linetype="dashed", alpha =.5) +
  geom_errorbar(alpha=.5, width=0) +
  geom_point(size=2.5, fill = "white") +
  scale_shape_manual(values=c(16, 21)) +
  # coord_fixed(ratio=1) +
  coord_cartesian(xlim=c(-.12,.08), ylim=c(-.12,.08)) +
  annotate(geom = "text", x = .05, y = -.08, 
           label = bquote(paste("r"["A"]*" = ", .(cor_val_A)))) +
  annotate(geom = "text", x = .05, y = -.105, 
           label = bquote(paste("r"["B"]*" = ", .(cor_val_B)))) +
  theme_bw(base_size=11) +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        legend.position = c(.2,.8),
        legend.background = element_rect(fill = NA)) +
  theme(aspect.ratio = 1) +
  labs(title = "B", y = "Observed change", x="Predicted change", 
       shape = "Experiment")

@@

_Holistic balance_, from McFadden et al.’s (2010) Complementary, Alternative, and Conventional Medicine Attitudes Scale (CACMAS) (Study 1: observed $\alpha$ = `r format(round(alpha_values$hb, 2), nsmall = 2)`)

@@

_Naturalism_ (Study 1: observed $\alpha$ = `r format(round(alpha_values$nat, 2), nsmall = 2)`)

@@

_Medical skepticism_ (Study 1: observed $\alpha$ = `r format(round(alpha_values$medSkept, 2), nsmall = 2)`)

@@

_Disease rarity_ (Study 1: observed $\alpha$ = `r format(round(alpha_values$diseaseRare, 2), nsmall = 2)`)

@@

_Disease severity_ (Study 1: observed $\alpha$ = `r format(round(alpha_values$diseaseSevere, 2), nsmall = 2)`)

@@

_Vaccine effectiveness_ (Study 1: observed $\alpha$ = `r format(round(alpha_values$vaccEff, 2), nsmall = 2)`)

@@

_Vaccine danger_ (Study 1: observed $\alpha$ = `r format(round(alpha_values$vaccDanger, 2), nsmall = 2)`)

@@

_Toxic additives in vaccines_ (Study 1: observed $\alpha$ = `r format(round(alpha_values$vaccTox, 2), nsmall = 2)`)

@@

_Infant immune system: Vaccines strain_ (Study 1: observed $\alpha$ = `r format(round(alpha_values$vaccStrain, 2), nsmall = 2)`)

@@

_Vaccination intentions_ (Study 1: observed $\alpha$ = `r format(round(alpha_values$vaccIntent, 2), nsmall = 2)`)

@@

_Parental expertise_ (Study 1: observed $\alpha$ = `r format(round(alpha_values$parentExpert, 2), nsmall = 2)`)

@@

_Infant immune system: Limited capacity_ (Study 1: observed $\alpha$ = `r format(round(alpha_values$infantImmLimCap, 2), nsmall = 2)`)

@@

_Infant immune system: Weakness_ (Study 1: observed $\alpha$ = `r format(round(alpha_values$infantImmWeak, 2), nsmall = 2)`)

@@

_Parental protectiveness_ (Study 1: observed $\alpha$ = `r format(round(alpha_values$overpar, 2), nsmall = 2)`)
